I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-27 Paper/comppaths.tex
section 3

In this section, we explore the key factor for the loss of accuracy in value abstraction methodologies. To this end, we first introduce a novel notion of compensating paths:

@@

The discussion so far shows  that compensation is one of the possible factors contributing to inaccuracy. We now establish that it is indeed the sole cause of inaccuracy, in particular,  if a DNN lacks any compensating path, then any methodology that is at least as accurate as the Box abstraction, such as ${\text{DeepPoly}}$ or LP, will precisely determine the exact upper and lower bounds for every node. This assertion is formalized in the following theorem:

>>>>

In this section, we explore the key factor for the loss of accuracy in value 
abstraction methodologies. To this end, we first introduce the novel notion of compensating paths:

@@

The discussion so far shows  that compensation is one of the possible factors contributing to inaccuracy. We now establish that it is the sole cause of inaccuracy:
if a DNN lacks any compensating path, then any methodology that is at least as accurate as the Box abstraction, such as LP and $\overline{\mbox{DeepPoly}}$ (but not DeepPoly), will precisely determine the exact upper and lower bounds for every node. This assertion is formalized in the following theorem:
